%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {CEO \& Founder} % Job title
    {Pinkerton Pickle Warehouse} % Organization
    {Dover, DE} % Location
    {Forever--Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a groundbreaking strategy for selling pickles to the unwilling.}
        \item {Pioneered pickle-based skincare (<Feel the burn! It means it's working!>)}
        \item {Lost thousands in overhead costs due to an unforseen cucumber surplus.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Editor-in-Chief} % Job title
    {CBH (Crusty Butthole) Magazine (The Feline Filth Authority)} % Organization
    {Dover, DE} % Location
    {2020--Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Revolutionized the highly controversial cat smut industry.}
        \item {Personally oversaw butthole photography quality control.}
        \item {Successfully avoided multiple lawsuits.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Dean of Academics} % Job title
    {Herverd University (Unaccredited, Unapologetic)} % Organization
    {REMOTE} % Location
    {2019--2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hand-selected all faculty.}
        \item {Authored every textbook, including <Lick First, Ask Questions Later>.}
        \item {Invented several degrees, including a Masters in Scamology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CEO} % Job title
    {BuyMyPoop.com} % Organization
    {REMOTE} % Location
    {2017--2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A promising startup with a niche audience.}
        \item {Shut down due to biohazard concerns.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder} % Job title
    {Cat Minx: The 24/7 Catertainment Channel} % Organization
    {REMOTE} % Location
    {2015--2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created groundbreaking feline TV programming <Birds: The Forbidden Channel>}
        \item {Produced record-breaking content, including <Pidgeons Don't Pluck Themselves>}
        \item {Secured zero investors.}
        \item {Collaborated with IT team on server maintenance and security implementations}
        \item {Provided direct technical support to research staff, ensuring minimal disruption to critical laboratory operations}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Self-Appointed Attorney} % Job title
    {Pinkerton Law Offices, Esq.} % Organization
    {REMOTE} % Location
    {2020--Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Specialized in "Loudly Arguing" as a defense strategy.}
        \item{Famously lost the case of Herverd University v. The Accreditation Board.}
        \item{Banned from multiple courthouses.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
